# Convert inputdata into phyloseq object

*r Biocpkg("phyloseq")* [@mcmurdie2013phyloseq] is the most popular [Biocondcutor](https://bioconductor.org/) package used by the microbiome research field, and `phyloseq-class` objects are a great data-standard for microbiota data in R. Therefore, the core functions in  `XMAS` take `phyloseq-class` object as input. In the phyloseq object, information on OTU abundances, taxonomy of OTUs, the phylogenetic tree and metadata is stored.


This tutorial will introduce you the basic steps to convert results from the in-house pipeline into *phyloseq-class object*. More importantly on how to look at your data and filter appropriately. We will use the inputs from **/home/xuxiaomin/project/standardized_analytics_workflow_R_function/demo_data/**.


**Loading packages**
```{r, echo=TRUE, results="hide", warning=FALSE, message=FALSE, fig.align="center"}
library(XMAS)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
library(ggpubr)
```


## Metaphlan2/3

The result of the in-house **[Metaphlan2/3](https://huttenhower.sph.harvard.edu/metaphlan2)** pipeline:

1. /home/xuxiaomin/project/standardized_analytics_workflow_R_function/demo_data/MGS/metaphlan2_merged.tsv

2. /home/xuxiaomin/project/standardized_analytics_workflow_R_function/demo_data/MGS/metadata.txt

```{r, warning=FALSE, message=FALSE}
metaphlan2_res <- read.table(
    system.file(
        "extdata", "metaphlan2_merged.tsv",
        package = "XMAS"
    ),
    header = TRUE, 
    stringsAsFactors = FALSE
)
metaphlan2_sam <- read.table(
    system.file(
        "extdata", "metaphlan2_metadata.tsv",
        package = "XMAS"
    ),
    sep = "\t",
    header = TRUE,
    stringsAsFactors = FALSE
)

metaphlan2_res_list <- import_metaphlan_taxa(metaphlan2_res, taxa_level = "Species")
otu_tab <- metaphlan2_res_list$abu_tab
tax_tab <- metaphlan2_res_list$tax_tab
sam_tab <- metaphlan2_sam %>% tibble::column_to_rownames("SampleID")

metaphlan2_ps <- import_metaphlan2(otu_tab = otu_tab, 
                                   sam_tab = sam_tab,
                                   tax_tab = tax_tab)
metaphlan2_ps
```

we obtain the **phyloseq-class object** and then use it to perform data analysis.

Here, the phyloseq object comprises five components (*OTU Table*, *Sample Data*, and *Taxonomy Table*).

##  Summarize phyloseq-class object
```{r, warning=FALSE, collapse=TRUE}
summarize_phyloseq(metaphlan2_ps)
```

Notice the **Sparsity (0.713)**, indicating the data has many zeros and pay attention to the downstream data analysis. A common property of amplicon based microbiota data generated by sequencing.

## Systematic Information
```{r}
sessionInfo()
```
