# Data processing



**Loading packages**

```R
library(XMAS)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
library(ggpubr)
```


This part has too may procedures and we only choose some of them. Please go to **Chapter 6** to see more approaches and details for being familiar with this part.

## Extracting specific taxonomic level
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_species <- summarize_taxa(metaphlan2_ps_NoQC, taxa_level = "Species")
metaphlan2_ps_species
```

## Filtering the low relative abundance or unclassified taxa by the threshold (total counts < 1e-4)
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_species_filter <- run_filter(metaphlan2_ps_species, cutoff = 1e-4, unclass = TRUE)
metaphlan2_ps_species_filter 
```

## Trimming the taxa with low occurrence less than threshold
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_species_filter_trim <- run_trim(metaphlan2_ps_species_filter, cutoff = 0.2, trim = "feature")
metaphlan2_ps_final <- metaphlan2_ps_species_filter_trim
metaphlan2_ps_final
```

Finally, we obtained the final phyloseq-class object _metaphlan2\_ps\_species\_filter\_trim_ and changed its name.

## Systematic Information
```{r}
sessionInfo()
```
