# Data processing


**Loading packages**

```{r, echo=TRUE, results="hide", warning=FALSE, message=FALSE}
library(XMAS2)
library(dplyr)
library(tibble)
library(phyloseq)
```


This part has too may procedures and we only choose some of them. Please go to **[XMAS tutorial: Chapter 6](https://xbiomeanalysis.github.io/XMAS_tutorial/pre-processing.html)** to see more approaches and details for being familiar with this part.

## Extracting specific taxonomic level

* Removing spike-in sample (BRS)
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_remove_BRS <- get_GroupPhyloseq(
                     ps = metaphlan2_ps,
                     group = "Group",
                     group_names = "QC",
                     discard = TRUE)
metaphlan2_ps_LOD_species_remove_BRS
```


* Species
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_LOD_species <- aggregate_LOD_taxa(metaphlan2_ps_remove_BRS, 
                                                taxa_level = "Species", 
                                                cutoff = 1e-04)
metaphlan2_ps_LOD_species
```

* Genus
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_LOD_genus <- aggregate_LOD_taxa(metaphlan2_ps_remove_BRS, 
                                              taxa_level = "Genus", 
                                              cutoff = 1e-04)
metaphlan2_ps_LOD_genus
```


* Phylum
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_LOD_phylum <- aggregate_LOD_taxa(metaphlan2_ps_remove_BRS, 
                                               taxa_level = "Phylum", 
                                               cutoff = 1e-04)
metaphlan2_ps_LOD_phylum
```

Finally, we obtained the final phyloseq-class object.


## Systematic Information
```{r}
devtools::session_info()
```
