# Microbial composition

**Loading packages**

```R
library(XMAS)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
library(ggpubr)
```


A whole picture of the microbial composition.

## Stacked barplot 

* **XMAS** package
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=7, fig.align="center", fig.cap="Microbial composition"}
plot_StackBarPlot(
        ps=metaphlan2_ps_final,
        taxa_level="Phylum",
        group = "Group",
        cluster = TRUE)
```

* **XVIZ** package
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=9, fig.align="center", fig.cap="Microbial composition in XVIZ"}
plot_stacked_bar(
        phyloseq = metaphlan2_ps_final,
        level = "Phylum",
        feature = "Group")
```

## Core microbiota
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=7, fig.align="center", fig.cap="Core taxa"}
prevalences <- seq(0.05, 1, 0.05)
detections <- 10^seq(log10(1e-3), log10(0.2), length = 10)

pl_core <- plot_core_taxa(metaphlan2_ps_final, 
                    plot.type = "heatmap", 
                    colours = gray(seq(0, 1, length=5)),
                    prevalences = prevalences, 
                    detections = detections, 
                    min.prevalence = 0.5)+
    xlab("Detection Threshold (Relative Abundance (%))")

pl_core
```

The degree of color indicates the size of abundance and prevalence.

* Use `core_members` to obtain the core taxa. detection for abundance and prevalence for occurrence.
```{r, warning=FALSE, message=FALSE}
core_taxa_name <- core_members(metaphlan2_ps_final, detection = 0.01, prevalence = 0.5)
print(core_taxa_name)
```

**Result**:

Only 4 genera (s__Bacteroides_uniformis, s__Bacteroides_vulgatus, s__Faecalibacterium_prausnitzii and s__Ruminococcus_sp_5_1_39BFAA) passed the threshold of detection and prevalence which we choose.

## Systematic Information
```{r}
sessionInfo()
```