# Differential Analysis


**Loading packages**

```{r, echo=TRUE, results="hide", warning=FALSE, message=FALSE}
library(XMAS2)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
library(ggpubr)
```


There are more than 10 approaches to perform differential analysis. Here, we choose two of them and recommend users going to **Chapter 10** to see more details.

## Filtering & Trimming

We suggest that filtering taxa with low abundance (the summarized value under cutoff: `1e-4`) and trimming taxa with low prevalence (default: `0.1`).

### Filtering the low relative abundance or unclassified taxa by the threshold (total counts < 1e-4)

* filter by sum relative abundance
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_species_filter <- run_filter(metaphlan2_ps_LOD_species_remove_BRS, cutoff = 1e-4, unclass = TRUE)
metaphlan2_ps_species_filter 
```

* filter by following two criterion [@thingholm2019obese]

> Species from taxonomic profiles were retained for further analysis if their mean relative abundance exceeded 0.005
(0.5%) across the dataset with a minimum abundance of 0.05 (5%) in at least one sample and non-zero abundance in at least
60% of samples. 

1. Mean relative abundance: 0.005; 

2. Minimum relative abundance: 0.05;

Here, we use 0.01 (the 1e-4 regarded as 0.01 compared to the Referece because Metaphlan2 data had been divided 100).
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_species_filter2 <- run_filter2(metaphlan2_ps_LOD_species_remove_BRS, cutoff_mean = 1e-04, cutoff_one = 1e-03, unclass = TRUE)
metaphlan2_ps_species_filter2
```


### Trimming the taxa with low occurrence less than threshold
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_species_filter_trim <- run_trim(metaphlan2_ps_species_filter, cutoff = 0.1, trim = "feature")
metaphlan2_ps_species_filter_trim
```

## Liner discriminant analysis (LDA) effect size (LEfSe)

* Calculation
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_lefse <- run_lefse(
                    metaphlan2_ps_species_filter_trim,
                    group = "Group",
                    group_names = c("AA", "BB"),
                    norm = "CPM",
                    Lda = 2)
head(metaphlan2_ps_lefse)
```

* Visualization
```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4, fig.align="center", fig.cap="Lefse analysis"}
# # don't run this code when you do lefse in reality
# metaphlan2_ps_lefse$LDA_Score <- metaphlan2_ps_lefse$LDA_Score * 1000
plot_lefse(
  da_res = metaphlan2_ps_lefse,
  x_index = "LDA_Score",
  x_index_cutoff = 1,
  group_color = c("green", "red"))
```


## Wilcoxon Rank-Sum test

* Calculation
```{r, warning=FALSE, message=FALSE}
metaphlan2_ps_wilcox <- run_wilcox(
                    metaphlan2_ps_species_filter_trim,
                    group = "Group",
                    group_names = c("AA", "BB"))

head(metaphlan2_ps_wilcox)
```


* Volcano
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.align="center", fig.cap="Wilcoxon Rank-Sum test"}
plot_volcano(
    metaphlan2_ps_wilcox,
    group_names = c("AA", "BB"),
    x_index = "Log2FoldChange (Rank)\nAA_vs_BB",
    x_index_cutoff = 0.5,
    y_index = "Pvalue",
    y_index_cutoff = 0.05,
    group_color = c("red", "grey", "blue"),
    topN = 4,
    taxa_name = "s__Megamonas_rupellensis")
```


## Dominant taxa

Display the significant taxa with selection using boxplot.

```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=10, fig.height=4, fig.cap="Dominant Taxa"}
plot_topN_boxplot(
    ps = metaphlan2_ps_species_filter_trim,
    da_res = metaphlan2_ps_wilcox,
    x_index = "Log2FoldChange (Rank)\nAA_vs_BB",
    x_index_cutoff = 0.5,
    y_index = "Pvalue",
    y_index_cutoff = 0.05,
    topN = 4,
    group = "Group")
```


## Multiple differential analysis by one function

Here, we provide the `run_multiple_da` for obtaining the results list from multiple differential analysis methods.

```{r, warning=FALSE, message=FALSE}
multiple_res <- run_multiple_da(
       metaphlan2_ps_species_filter_trim,
       group = "Group",
       group_names = c("AA", "BB"),
       da_method = c("wilcox", "limma_voom", "ttest"))

names(multiple_res)
```

* plot  results
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=13, fig.cap="Multiple DA results"}
plot_multiple_DA(
  Multip_DA_res = multiple_res,
  x_index_list = c("Log2FoldChange (Rank)\nAA_vs_BB", "logFC", "Log2FoldChange (geometricmean)\nAA_vs_BB"),
  x_index_cutoff = 0,  
  y_index = "Pvalue",
  y_index_cutoff = 0.5,
  cellwidth = 35,
  cellheight = 10,
  fontsize_number = 15)
```


## Systematic Information
```{r}
devtools::session_info()
```

